---
output: 
  pdf_document: 
    number_sections: true
    includes:
      before_body: '../TeX/preamble.tex'
      in_header: '../Tex/header.tex'
    extra_dependencies: ['changepage']
    keep_tex: true
    latex_engine: xelatex
monofont: Lucida Console
mainfont: Times New Roman
#fontsize: 11pt
---

\vspace{.25in}

<!-- 1. COURSE INFORMATION -->

\section{Concact Information}
```{r contact_info, child = "01_Course_Information/01_contact_info.Rmd"}
```

\subsection{Description}
```{r description, child = "01_Course_Information/02_description.Rmd"}
```

\subsection{Meeting}
```{r meeting, child = "01_Course_Information/03_meeting_dates.Rmd"}
```

\subsection{Advanced Academic Activity}
```{r advanced_activity, child = "01_Course_Information/04_advanced_activity.Rmd"}
```

\subsection{Course Objectives}
```{r objectives, child = "01_Course_Information/05_course_objectives.Rmd"}
```

\subsection{Student Learning Objectives}
```{r slos, child = "01_Course_Information/06_student_learning_outcomes.Rmd"}
```

\subsection{Credit Hour(s)}
```{r credits, child = "01_Course_Information/07_credit_hour.Rmd"}
```

\subsection{Readings}
```{r readings, child = "01_Course_Information/08_readings.Rmd"}
```

<!-- \subsection{Required Software} -->
<!-- ```{r software, child = "01_Course_Information/09_required_software.Rmd"} -->
<!-- ``` -->

\subsection{Academic Integrity}
```{r integrity, child = "01_Course_Information/10_academic_integrity.Rmd"}
```

\subsection{Disabled Student Services and Accomodations}
```{r ada, child = "01_Course_Information/11_disabled_students.Rmd"}
```

\subsection{Course Structure}
```{r structure, child = "01_Course_Information/12_class_structure.Rmd"}
```

\subsection{Course Communication}
```{r communication, child = "01_Course_Information/13_course_communication.Rmd"}
```


<!-- 2. COURSE REQUIREMENTS -->

\section{Course Requirements}

\subsection{Individual Assignments}

\subsubsection{Journal Article Critique}
```{r ass_a, child = "02_Course_Requirements/01_critiques.Rmd"}
```

<!-- \subsubsection{Special Topics Team Presentation} -->
<!-- ```{r ass_b, child = "02_Course_Requirements/02_presentations.Rmd"} -->
<!-- ``` -->

<!-- \subsubsection{Individual Data Analysis Lab Assignments} -->
<!-- ```{r ass_k, child = "02_Course_Requirements/03_labs.Rmd"} -->
<!-- ``` -->

<!-- \subsubsection{Chapter 3 in a Nutshell} -->
<!-- ```{r ass_k, child = "02_Course_Requirements/04_chapter_3.Rmd"} -->
<!-- ``` -->

\subsubsection{Practivce Quantitative Qualifying Exam}
```{r ass_k, child = "02_Course_Requirements/05_qualifying_exam.Rmd"}
```

\subsection{Grade Calculation}
```{r grade_calc, child = "02_Course_Requirements/06_grade_calculation.Rmd"}
```


<!-- 3. POLICIES -->

\section{Policies}

<!-- \subsection{Attendance} -->
<!-- ```{r att, child = "03_Policies/01_attendance.Rmd"} -->
<!-- ``` -->

\subsection{Late Work}
```{r late_work, child = "03_Policies/02_late_work.Rmd"}
```


<!-- 4. Disclaimer -->

\section{Disclaimer}

```{r decorum, child = "04_Disclaimer/01_disclaimer.Rmd"}
```


<!-- 5. COURSE CALENDAR -->

```{r calendar, child = "05_Course_Calendar/01_course_calendar.Rmd"}
```

<!-- 6. CALENDAR OF DUE DATES-->

```{r calendar, child = "05_Course_Calendar/02_due_dates.Rmd"}
```


<!-- 7. COVID STUFF -->s
\section{CruFlex and Other Pandemic-Related Details}
```{r cruflex, child = "07_COVID/01_covid.Rmd"}
```

<!-- CRU PLEDGE -->
```{r cruflex, child = "07_COVID/02_crupledge.Rmd"}
```

